A pipeline to analyse time-course gene expression data

### 2019-05-13 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

\begin{itemize}
\tightlist
\item
  Add legends to the plots that don't have.
\item
  Currently have two functions ``plot\_genes'', ``plot\_centroids'', that do exactly
  the same thing. Find a better name for both of them
\end{itemize}

@@

>>>>

\begin{itemize}
\tightlist
\item
  Add legends to the plots that don't have.
\item
  Currently have two functions ``plot\_genes'', ``plot\_centroids'', that do exactly
  the same thing. Find a better name for both of them
\item
  switch to camel case function names
\item
  shorten function names
\item
  Remove the namespace call
\item
  Move the normalization to a supplementary data
\item
  Make clear that it applies to RNASeq and how to call the different functions
  toRNASeq
\item
  Check that clustering can deal with count data.
\end{itemize}

@@

\textbf{Add a helper function to make the contrasts for timely DE}
